### 2016-04-01 text/ms.Rmd
Remove the ROC section from the main text

Predictive performance can be evaluated with metrics that represent a variety of modelling goals. For continuous response variables such as the mean and slope of population status, performance metrics often measure some form of bias, precision, accuracy (a combination of bias and precision), or the ability to correctly rank or correlate across populations [e.g. @walther2005]. Here, we measure proportional error, defined as $(\hat{b} - b)/\abs{b}$, where $\hat{b}$ and $b$ represent estimated and 'true' (or stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median proportional error to measure bias, median absolute proportional error to measure accuracy, and Spearman's rank-order correlation between predicted and 'true' values to measure the ability to correctly rank populations. When cross-validating against the RAM Legacy Stock Assessment database, we treated the estimates from these data-rich stock assessments as known without error. Thus, any error in the stock-assessment estimates of the mean or slope of $B/B_\mathrm{MSY}$ also contributes to our estimates of prediction error for each of the four data-limited models and the ensembles. We measured the ability for each model to correctly place stocks into categories of above or below $B/B_\mathrm{MSY} = 0.5$ at any decision threshold <!-- Jess: not sure what this means - at any decision threshold--> by plotting receiver operating characteristic curves; a threshold of $B/B_\mathrm{MSY} = 0.5$ is used to classify a stock as overfished in Australia and the United States [@daff2007; @hilborn2010]. Code to reproduce our analysis and an R package to fit the data-limited assessment models are available at <https://github.com/datalimited/...> (*Private while in review*).

@@

Ensemble methods, and in particular the machine learning superensemble models (random forest and GBM), generally improved estimates of status and trend over any individual model (Fig. \ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h). Compared to the individual models, machine learning superensembles improved accuracy (median absolute proportional error) by `r mean_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from `r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and reduced bias (median proportional error) from `r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range` (Fig. \ref{performance}a). These superensembles also generally had better ability to distinguish if simulated stocks were above or below $B/B_\mathrm{MSY} = 0.5$ (Fig. \ref{roc-sim}). Results were similar when predicting trend: compared to individual models, machine learning superensembles improved accuracy by `r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from `r slope_sim$ind_corr_range` to `r slope_sim$mach_corr_range`, and reduced bias from `r slope_sim$ind_mre_range` to `r slope_sim$mach_mre_range` (Fig. \ref{performance-sim-slope}). The ensemble models that simply took a mean of the individual models ranked slightly behind the best individual model for estimating fish stock status (CMSY; Fig. \ref{performance}a) and had slightly lower correlation but higher accuracy than the best individual model at predicting the trends of status (SSCOM; Fig. \ref{performance-sim-slope}).

>>>>

Predictive performance can be evaluated with metrics that represent a variety of modelling goals. For continuous response variables such as the mean and slope of population status, performance metrics often measure some form of bias, precision, accuracy (a combination of bias and precision), or the ability to correctly rank or correlate across populations [e.g. @walther2005]. Here, we measure proportional error, defined as $(\hat{b} - b)/\abs{b}$, where $\hat{b}$ and $b$ represent estimated and 'true' (or stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median proportional error to measure bias, median absolute proportional error to measure accuracy, and Spearman's rank-order correlation between predicted and 'true' values to measure the ability to correctly rank populations. When cross-validating against the RAM Legacy Stock Assessment database, we treated the estimates from these data-rich stock assessments as known without error. Thus, any error in the stock-assessment estimates of the mean or slope of $B/B_\mathrm{MSY}$ also contributes to our estimates of prediction error for each of the four data-limited models and the ensembles. Code to reproduce our analysis and an R package to fit the data-limited assessment models are available at <https://github.com/datalimited/ensembles> (*Private while in review*).

@@

Ensemble methods, and in particular the machine learning superensemble models (random forest and GBM), generally improved estimates of status and trend over any individual model (Fig. \ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h). Compared to the individual models, machine learning superensembles improved accuracy (median absolute proportional error) by `r mean_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from `r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and reduced bias (median proportional error) from `r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range` (Fig. \ref{performance}a). Results were similar when predicting trend: compared to individual models, machine learning superensembles improved accuracy by `r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from `r slope_sim$ind_corr_range` to `r slope_sim$mach_corr_range`, and reduced bias from `r slope_sim$ind_mre_range` to `r slope_sim$mach_mre_range` (Fig. \ref{performance-sim-slope}). The ensemble models that simply took a mean of the individual models ranked slightly behind the best individual model for estimating fish stock status (CMSY; Fig. \ref{performance}a) and had slightly lower correlation but higher accuracy than the best individual model at predicting the trends of status (SSCOM; Fig. \ref{performance-sim-slope}).
